Tempo and mode of promoter evolution as observed in the \textit{Paramecium aurelia} species complex

### 2020-06-30 manuscript.tex
Added more material to the introduction.

%\history{Received xx xxxxx 2019; reviews returned xx xxxx 2019; accepted xx xxxxx 2019}

@@

\abstract{Goes here
}

@@

Main et al. \citep{Main:2013dg}, used TSS profiling information generated in \textit{D. melanogaster} to identify putative orthologous TSSs in three other \textit{Drosophila} taxa.

>>>>

%\history{Received xx xxxxx 2020; reviews returned xx xxxx 2020; accepted xx xxxxx 2020}

@@

\abstract{Goes here}

@@

Main et al. \citep{Main:2013dg}, used a separate TSS profiling method in \textit{D. melanogaster} to identify putative orthologous TSSs in three other \textit{Drosophila} taxa: \textit{D. simulans}, \textit{D. pseudoobscura} and \textit{D. sechellia}. The authors found that the location and estimated activities of orthologous TSSs to be generally conserved, but did observe instances of TSS variation that suggest new promoters. Notably, Main \textit{Main et. al.} found species-specific differences in the alcohol dehydrogenase (ADH) gene among the four species. 
